LOSA Fuel Poverty maps

### 2021-08-29 LSOA Fuel poverty.Rmd
Using the maps for the mapping discussion section

```{r Mapping the LSOA 2019 Fuel Poverty}
lsoa_fuelpov_2019$LSOA11CD <- lsoa_fuelpov_2019$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov_2019_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2019) #merging these
# as above - why does it load as a char?
lsoa_fuelpov_2019_merged$pcFP <- as.numeric(lsoa_fuelpov_2019_merged$`Proportion of households fuel poor (%)`)
ggplot2::ggplot(lsoa_fuelpov_2019_merged) +
  geom_sf(aes(fill=pcFP))+ 
  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
```
#####Looking at the cities in more detail
```{r Southampton LSOA Fuel Pov 2019}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Southampton")

@@

# plotting the change in fuel poverty from 2018-2012 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Winchester")
```

>>>>

```{r Mapping the LSOA 2019 Fuel Poverty}
lsoa_fuelpov_2019$LSOA11CD <- lsoa_fuelpov_2019$"LSOA Code" #creating a variable with the LSOA code in the same name as in sf_data
lsoa_fuelpov_2019_merged <- merge(lsoa_sf_data, lsoa_fuelpov_2019) #merging these
# as above - why does it load as a char?
lsoa_fuelpov_2019_merged$pcFP <- as.numeric(lsoa_fuelpov_2019_merged$`Proportion of households fuel poor (%)`)
ggplot2::ggplot(lsoa_fuelpov_2019_merged) +
  geom_sf(aes(fill=pcFP))+ 
  scale_fill_continuous(name="Proportion of households fuel poor (%)", low="green",high="red")+
  labs(caption ="Solent (all LSOAs)")
head(lsoa_fuelpov_2019_merged)
names(lsoa_fuelpov_2019_merged)
```
#####Looking at the cities in more detail
```{r Southampton LSOA Fuel Pov 2019}
#Cities such as Southampton disappear due to their density, we will now map Southampton alone to see this area in more detail
mapData <- dplyr::filter(lsoa_fuelpov_2019_merged, LAD11NM == "Southampton")

@@

# plotting the change in fuel poverty from 2018-2012 of Winchester in more detail
ggplot2::ggplot(mapData) + 
  geom_sf(aes(fill = pc_diff)) +
  scale_fill_continuous(name = "Change in Proportions of households fuel poor (%)", low = "green", high = "red") +
  labs(caption = "Winchester")
```
### Over 65 annd Fuel Poverty
```{r Loading in the Census age data}
inFile<-paste0(dataFolder, "census/KS102EW-age-categories.csv")
census_age<-readr::read_csv (inFile)
census_age$'Local Authority Code'<- census_age$'geography code'
head(census_age)
names(census_age)
```
```{r Mapping the fuel poverty in over 65s}
#census_age$"LSOA11CD" <- census_age$"geography code"
Census_age_fp <- merge(lsoa_fuelpov_2019_merged, census_age)
names(Census_age_fp)
ggplot(Census_age_fp, aes(x='Proportion Over 65', y=pcFP))

```
